The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-23 paper/paper.tex
paper: lots of miscellanous progress

% Some abbreviations
\newcommand{\tl}{\ensuremath{\mathsf{tl}}}
\newcommand{\hd}{\ensuremath{\mathsf{hd}}}
\newcommand{\imp}{\rightarrow}
\newcommand{\overright}[1]{\overrightarrow{#1}}
\renewcommand{\D}{D}
\newcommand{\hdD}{D.1}
\newcommand{\tlD}{D.2}
\renewcommand{\d}{d}
\renewcommand{\E}{E}
\renewcommand{\l}{l}
\renewcommand{\c}{c}
\newcommand{\pair}[2]{#1, #2}
\newcommand{\Dom}{\textsf{Dom}}
\newcommand{\UIP}{\textsf{UIP}}

@@

\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
\renewcommandx{\cohf}[6][1,2,3,4,5,6]{\coh{frame}[][#3][#4][#5][#6][#1,#2][][]}
\renewcommandx{\cohl}[6][1,2,3,4,5,6]{\coh{layer}[][#3][#4][#5][#6][#1,#2][][]}
\renewcommandx{\cohp}[6][1,2,3,4,5,6]{\coh{painting}[][#3][#4][#5][#6][#1,#2][][]}

@@

The definition of $\framep[n+1][p]$ also depends, via $\layer[n][p-1]$, on $\painting[n][p-1]$. Both via $\painting[n][p-1]$ and $\restrf[n][p-1]$, it depends also on $\framep[n][p-1]$ by typing dependency. This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][p-1]$.
Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    \framep[n+1][\lbrack 0,p \rbrack] \arrow[d] \arrow[ddr]\\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,p-1]$}"', near start, shift right=2mm, hook']\\
  \end{tikzcd}
\end{center}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][\lbrack 0,p-1 \rbrack] &  & :      & \U                                               \\
    \frametype[n]                        &  & \defeq & \unittype                                        \\
    \frametype[n][\lbrack 0,p \rbrack]   &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \paintingtype[n][\lbrack 0,p-1 \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]) & :      & \U                                                                                                                   \\
    \paintingtype[n]                        & \unitpoint                                                             & \defeq & \unittype                                                                                                            \\
    \paintingtype[n][\lbrack 0,p \rbrack]   & (\framep[n][\lbrack 0,p \rbrack])                                      & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
  \end{array}
\end{equation*}

@@

Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][\lbrack p,n+1 \rbrack]$, $\painting[n][\lbrack p,n \rbrack]$, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$. Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n+1][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$ respectively depend on the earlier values $\framep[n+1][\lbrack 0,p-1 \rbrack]$, $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    & & \painting[n+1][\lbrack p,n+1 \rbrack] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n+1][\lbrack 0,p-1 \rbrack]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n+1][\lbrack p,n+1 \rbrack]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] & &
    \painting[n][\lbrack p,n-1 \rbrack] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \udensdash{\restrf[n][\lbrack 0,p-1 \rbrack]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n][\lbrack p,n \rbrack] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n+1][\lbrack p,n \rbrack]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

Let us introduce another abbreviation to combine a full $\deps[n][\lbrack 0,n \rbrack]:\depstype[n][\lbrack 0,n \rbrack]$ with a family $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U$:
\begin{align*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
            \deps[n][\lbrack 0,n \rbrack] & : & \depstype[n][\lbrack 0,n \rbrack]                               \\
            E                             & : & \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n+1][p]$ for $p \leq n+1$ by recursion on $n-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][p]               &
    (\fulldeps[n]:\fulldepstype[n]) & :      & \paintingtype[n+1][p]      \\
    \painting[n+1][n+1]             &
    \fulldeps[n]                    & \defeq & \fulldeps.E                \\
    \painting[n+1][p \leq n]        &
    \fulldeps[n]                    & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack]). \\
              \painting[n+1][p+1]
              (\fulldeps[n])(d,l)                                             \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
    \painting[n+1]                        &
    \fulldeps[n]                          & \defeq & \unittype                                                                                                                 \\
    \painting[n+1][\lbrack 0,p \rbrack]   &
    \fulldeps[n]
                                          & \defeq &
    (\painting[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                                                    \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \U                                                                \\
    \restrptype[n]                        & E      & \defeq                                                & \unittype \\
    \restrptype[n][\lbrack 0,p \rbrack]   &
    (\fulldeps[n])
                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times \left(
    \begin{array}{l}
        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                                 \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                            \\
  \end{array}
\end{equation*}

@@

We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$:
\begin{align*}
  \fulldepscohstype[n] \defeq
  \left(\begin{array}{lcl}
            \depscohs[n][\lbrack 0,n-1 \rbrack] & : & \depscohstype[n][\lbrack 0,n \rbrack]                                                \\
            E                                   & : & \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]))\rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n+1][\lbrack 0,p-1 \rbrack]     &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
    \restrp[n+1]                            &
    \fulldepscohs[n]                        & \defeq & \unittype                                                                      \\
    \restrp[n+1][\lbrack 0,p \rbrack]       &
    \fulldepscohs[n]
                                            & \defeq &
    (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                         \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                                           \\
    \cohptype[n]                        & \unitpoint                              & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,p \rbrack]   & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                        &                                         &        & \;\;\;\;\left\{
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
      \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =                                                                                                                                                                                             \\
      \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf[n+1][p](d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                                               \\
  \end{array}
\end{equation*}

@@

              \cohp[n][0,...p-1] & : & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\

@@

    \cohttype[n][p]                                                               &
    \fulldepscohs[n]                                                              & \defeq                                                                        &
              \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\
              \fulldepscohs.\depscohs.\cohf[n][p][r][0][\omega][\theta] \circ \cohf[n+1][p][q+1][0][\epsilon][\theta]
              (\fulldepscoht[n])
              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][r][\epsilon][\omega] =      \\
              \cohf[n+1][p][q+1][r+1][\epsilon][\omega]
              (\fulldepscoht[n])
              \circ \fulldepscohs.\depscohs.\cohf[n][p][q][0][\epsilon][\theta]
              \circ \cohf[n+1][p][r][0][\omega][\theta]
              (\fulldepscoht[n])                                                       \\

@@

    \cohl[n][p]                                                                   &
    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                             &
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                          \\
      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
    \end{array}                                                                                                                                                          \\
    \cohl[n][p][q][r][\epsilon][\omega]                                           &
    (\depscoht[n][\lbrack 0,p-1 \rbrack])                                         & \defeq                                                                        &
    \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\depscoht.\fulldepscohs[n])}{(\depscoht.\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                                                                                   \\
  \end{array}
\end{equation*}
We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
\begin{align*}
  \fulldepscohttype[n] \defeq
  \left(\begin{array}{lll}
            \depscoht[n][\lbrack 0,n \rbrack] & : & \depscohttype[n][\lbrack 0,n \rbrack]                                                                      \\
            E                                 & : & \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack])))\rightarrow \U \\
          \end{array}\right)
\end{align*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohp[n+1][\lbrack 0,p-1 \rbrack]       &
    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
    \cohp[n+1]                              &
    \fulldepscohs[n]                        & \defeq & \unittype                                                                        \\
    \cohp[n+1][\lbrack 0,p \rbrack]         &
    \fulldepscoht[n]
                                            & \defeq &
    (\cohp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht[n]),\cohp[n+1][p](\fulldepscoht[n]))                                               \\
  \end{array}
\end{equation*}

>>>>

% Some abbreviations
\newcommand{\tl}{\ensuremath{\mathsf{tl}}}
\newcommand{\hd}{\ensuremath{\mathsf{hd}}}
\newcommand{\imp}{\rightarrow}
\newcommand{\overright}[1]{\overrightarrow{#1}}
\newcommand{\ap}{\mathsf{ap}\;}
\renewcommand{\D}{D}
\newcommand{\hdD}{D.1}
\newcommand{\tlD}{D.2}
\renewcommand{\d}{d}
\renewcommand{\E}{E}
\renewcommand{\l}{l}
\renewcommand{\c}{c}
\newcommand{\pair}[2]{#1, #2}
\newcommand{\Dom}{\textsf{Dom}}
\newcommand{\UIP}{\textsf{UIP}}

@@

\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
\renewcommandx{\cohf}[6][1,2,3,4,5,6]{\coh{frame}[][#3][#4][#5][#6][#1][#2][]}
\renewcommandx{\cohl}[6][1,2,3,4,5,6]{\coh{layer}[][#3][#4][#5][#6][#1][#2][]}
\renewcommandx{\cohp}[6][1,2,3,4,5,6]{\coh{painting}[][#3][#4][#5][#6][#1][#2][]}

@@

The definition of $\framep[n+1][p]$ also depends, via $\layer[n][p-1]$, on $\painting[n][p-1]$. Both via $\painting[n][p-1]$ and $\restrf[n][p-1]$, it depends also on $\framep[n][p-1]$ by typing dependency. This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][p-1]$.
Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
\begin{center}
  \begin{tikzcd}
    \framep[n+1][\lbrack 0,p \rbrack] \arrow[d] \arrow[ddr]\\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,p-1]$}"', near start, shift right=2mm, hook']\\
  \end{tikzcd}
\end{center}

@@

\begin{equation*}
  \begin{array}{llcl}
    \frametype[n][\lbrack 0,p-1 \rbrack] &  & :      & \U                                               \\
    \frametype[n]                        &  & \defeq & \unittype                                        \\
    \frametype[n][\lbrack 0,p \rbrack]   &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \paintingtype[n][\lbrack 0,p-1 \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]) & :      & \U                                                                                                                   \\
    \paintingtype[n]                        & \unitpoint                                                             & \defeq & \unittype                                                                                                            \\
    \paintingtype[n][\lbrack 0,p \rbrack]   & (\framep[n][\lbrack 0,p \rbrack])                                      & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
  \end{array}
\end{equation*}

@@

Defining $\painting[n+1][p]$ for $p \leq n+1$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][\lbrack p,n+1 \rbrack]$, $\painting[n][\lbrack p,n \rbrack]$, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$. Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n+1][\lbrack p,n+1 \rbrack]$, $\framep[n+1][\lbrack p,n \rbrack]$ and $\restrf[n][\lbrack p,n \rbrack]$ respectively depend on the earlier values $\framep[n+1][\lbrack 0,p-1 \rbrack]$, $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
\begin{center}
  \begin{tikzcd}
    & & \painting[n+1][\lbrack p,n+1 \rbrack] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n+1][\lbrack 0,p-1 \rbrack]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n+1][\lbrack p,n+1 \rbrack]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] & &
    \painting[n][\lbrack p,n-1 \rbrack] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \udensdash{\restrf[n][\lbrack 0,p-1 \rbrack]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n][\lbrack p,n \rbrack] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n+1][\lbrack p,n \rbrack]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

Let us introduce another abbreviation to combine a full $\deps[n][\lbrack 0,n \rbrack]:\depstype[n][\lbrack 0,n \rbrack]$ with a family $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U$:
\begin{gather*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
      \deps[n][\lbrack 0,n \rbrack] & : & \depstype[n][\lbrack 0,n \rbrack]                               \\
      E                             & : & \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U \\
    \end{array}\right)
\end{gather*}

TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n+1][p]$ for $p \leq n+1$ by recursion on $n-p$:
\begin{equation*}
  \begin{array}{llcl}
    \painting[n+1][p]               &
    (\fulldeps[n]:\fulldepstype[n]) & :      & \paintingtype[n+1][p]      \\
    \painting[n+1][n+1]             &
    \fulldeps[n]                    & \defeq & \fulldeps.E                \\
    \painting[n+1][p \leq n]        &
    \fulldeps[n]                    & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack]). \\
              \painting[n+1][p+1]
              (\fulldeps[n])(d,l)                                             \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \painting[n+1][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
    \painting[n+1]                        &
    \fulldeps[n]                          & \defeq & \unittype                                                                                                                 \\
    \painting[n+1][\lbrack 0,p \rbrack]   &
    \fulldeps[n]
                                          & \defeq &
    (\painting[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                                                    \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \restrptype[n][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \U                                                                \\
    \restrptype[n]                        & E      & \defeq                                                & \unittype \\
    \restrptype[n][\lbrack 0,p \rbrack]   &
    (\fulldeps[n])
                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times \left(
    \begin{array}{l}
        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                                 \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                            \\
  \end{array}
\end{equation*}

@@

We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$:
\begin{equation*}
  \fulldepscohstype[n] \defeq
  \left(\begin{array}{lcl}
      \depscohs[n][\lbrack 0,n-1 \rbrack] & : & \depscohstype[n][\lbrack 0,n \rbrack]                                                \\
      E                                   & : & \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]))\rightarrow \U \\
    \end{array}\right)
\end{equation*}
TODO: say the convention on projection in the Introduction

@@

\begin{align*}{4}
  \restrp[n+1][\lbrack 0,p-1 \rbrack]     &
  (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
  \restrp[n+1]                            &
  \fulldepscohs[n]                        & \defeq & \unittype                                                                      \\
  \restrp[n+1][\lbrack 0,p \rbrack]       &
  \fulldepscohs[n]
                                          & \defeq &
  (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                         \\
\end{align*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                                           \\
    \cohptype[n]                        & \unitpoint                              & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,p \rbrack]   & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                        &                                         &        & \left\{
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                                                    \\
      \Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
      \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =                                                                                                                                  \\
      \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf[n+1][p](d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                                               \\
  \end{array}
\end{equation*}

@@

              \cohp[n][\lbrack 0,p-1 \rbrack] & : & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \\

@@

@@

    \cohl[n][p]                                                                   &
    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                             &
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                          \\
      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
    \end{array}                                                                                                                                                          \\
    \cohl[n][p][q][r][\epsilon][\omega]                                           &
    (\depscoht[n][\lbrack 0,p-1 \rbrack])                                         & \defeq                                                                        &
    \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\depscoht.\fulldepscohs[n])}{(\depscoht.\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                                                                                   \\
  \end{array}
\end{equation*}
where $\cohttype$ is:
\begin{equation*}
  \cohttype[n][p](\fulldepscohs[n]) \defeq
  \begin{array}{l}
    \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.                         \\
    \fulldepscohs.\depscohs.\cohf[n][p][r][0][\omega][\theta](\restrf[n+1][p][q+2][\epsilon]) \circ \\
    \ap\restrf[n][p][r][\omega](\cohf[n+1][p][q+1][0][\epsilon][\theta]
    (\fulldepscoht[n]))
    \circ                                                                                           \\
    \fulldepscohs.\depscohs.\cohf[n][p][q][r][\epsilon][\omega](\restrf[n+1][p][0][\theta]) =       \\
    \ap\restrf[n][p][0][\theta](\cohf[n+1][p][q+1][r+1][\epsilon][\omega]
    (\fulldepscoht[n]))
    \circ                                                                                           \\
    \fulldepscohs.\depscohs.\cohf[n][p][q][0][\epsilon][\theta](\restrf[n+1][p][r+1][\omega])
    \circ                                                                                           \\
    \ap\restrf[n][p][q][\epsilon](\cohf[n+1][p][r][0][\omega][\theta]
    (\fulldepscoht[n]))
  \end{array}
\end{equation*}

It is also convenient to introduce a notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
\begin{equation*}
  \fulldepscohttype[n] \defeq
  \left(\begin{array}{lll}
      \depscoht[n][\lbrack 0,n \rbrack] & : & \depscohttype[n][\lbrack 0,n \rbrack]                                                                      \\
      E                                 & : & \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack])))\rightarrow \U \\
    \end{array}\right)
\end{equation*}

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohp[n+1][\lbrack 0,p-1 \rbrack]       &
    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      & \cohptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht.\depscoht.\fulldepscohs[n])) \\
    \cohp[n+1]                              &
    \fulldepscohs[n]                        & \defeq & \unittype                                                                        \\
    \cohp[n+1][\lbrack 0,p \rbrack]         &
    \fulldepscoht[n]
                                            & \defeq &
    (\cohp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscoht[n]),\cohp[n+1][p](\fulldepscoht[n]))                                               \\
  \end{array}
\end{equation*}
